\chapter*{Abstract}

\noindent 
This study proposes the application of artificial intelligence (AI) techniques in the realm of the financial market, aiming to strategically predict and recommend investments. The work begins with a historical review of financial markets, addressing the efficient market theory, which posits that prices reflect all available information, also highlighting the influence of emotions and behaviors in shaping stock prices. An investigation into the efficiency of emerging markets reveals investment opportunities due to systematic deviations in prices.
Literature is examined to emphasize the evolution of technical, fundamental, quantitative, and sentiment analysis models. The study then reviews various AI techniques applied to forecasting financial assets, including linear models and those grounded in AI. The proposed methodology encompasses the extraction, generation, and selection of variables, culminating in the implementation of a prediction machine that combines statistical, classification, and regression models through ensemble techniques.
The results suggest the feasibility of achieving significant returns through forecasting techniques, with the prediction machine favorably compared to the buy-and-hold strategy. This integrative approach proves promising for guiding more informed and strategic financial decisions in the market.
\vfill%
\noindent Keywords: Stock prediction; Financial market; Artificial intelligence; Time series; Financial data analysis; Ensemble.

